### 2009-02-19 doc/ws-programming-tutorial/doc/tex_introduction/introduction.tex
Pushed the state of the chapter time service a little bit further - added a comment in introduction - modified some source code to have LaTeX labels

\subsection{The Arcecho service}
\task{Maybe the word tag needs to be replaced by the word element...}
\task{Where is the xsd file for HED configuration files??}
The first example shall give a basic understanding in how to configure the HED. The task is to setup the ARC intern Echo Web Service which has to be done by invoking the \textit{arched} daemon with a fitting HED configuration file. Such a fitting HED configuration file is shown in Listing~\ref{lst:arched_arcecho_xml}. It is written in XML and its structure is based on the \textcolor{urgent}{??} schema.
\lstsetARCHEDXML\\
\begin{program}
\centering
\lstinputlisting
	[
	label=lst:arched_arcecho_xml,
	caption={[HED configuration. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/arched_arcecho.xml}
\end{program}
The first line of the XML file contains the XML declartion. Several attributes can be defined here but at least the XML version should be specified. \task{What is this ArcConfig for??} % configuration namespaces
The \textit{Server} tag, to be found at line~\ref{lst_code:arched_arcecho_Server}, provides basic settings for the daemon such as location of the Pid-file or the Log-file.
The \textit{ModuleManager} holds the path to the plugin libraries. Several paths may be defined here. Due to the fact that the first library fitting to the plugin name is loaded, the order is relevant. The path should be at least assigned to the ARC installation directory. % for the standard MCC are defined here
The next set of tags are holding the name of the plugins to be loaded (line~\ref{lst_code:arched_arcecho_Plugins}).
The names have to correspond to the name of the dynamic libraries within the path defined by the \textit{ModuleManager}.
Finally the chain of the components are declared initiate with the tag \textit{Chain}.
Each component inside the chain is represented by a tag called \textit{Component} which has at least a name attribute.
Its important that a plugin has been loaded which provides the functionality of it.
Depending on the component certain additional tags may be defined inside of it.
\task{Internet Protocol is required.}
The first component of the chain is the \textit{tcp.service}. As to be seen the port 60000 gets assigned for the server to listen to.
The stream which is received by this component is passed to the component defined by the \textit{next} tag.
In that case the will be passed to the component with the \textit{id} atrribute named \textit{http}. According to this manner the message will be passed to higher layers until it reaches the \textit{Plexer}  Depending on the path of the URL which was demanded by the HTTP the Plexer multiplexes the request to the right Web Service. The path declared within the \textit{next} tag is a regular expression and leads to the service with the id named \textit{echo}. This service finally will process the message and create a new message which will be returned all the way back to the TCP layer. The Echo Web Service itself is provided by the ARC package. Additional fix parameters can be passed by assigning tags which have to be known to the Web Service.
The tags \textit{echo:prefix} and \textit{echo:suffix} seen in this example are defining the characters which will enclose the echo  returned string.
\task{The images of the HED structure always are ordered like: TCP - TLS - HTTP - PLEXER - SOAP - WEB SERVICE   but the source code examples are: TCP - TLS - HTTP - SOAP - PLEXER - WEB SERVICE}\\

>>>>

\subsection{The Arcecho service}
\task{Maybe the word tag needs to be replaced by the word element...}
\task{Where is the xsd file for HED configuration files??}
The first example shall give a basic understanding in how to configure the HED. The task is to setup the ARC intern Echo Web Service which has to be done by invoking the \textit{arched} daemon with a fitting HED configuration file. Such a fitting HED configuration file is shown in Listing~\ref{lst:arched_arcecho_xml}. It is written in XML and its structure is based on the \textcolor{urgent}{??} schema.
\lstsetARCHEDXML\\
\begin{program}
\centering
\lstinputlisting
	[
	label=lst:arched_arcecho_xml,
	caption={[HED configuration. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/arched_arcecho.xml}
\end{program}
The first line of the XML file contains the XML declartion. Several attributes can be defined here but at least the XML version should be specified. \task{What is this ArcConfig for??} % configuration namespaces
The \textit{Server} tag, to be found at line~\ref{lst_code:arched_arcecho_Server}, provides basic settings for the daemon such as location of the Pid-file or the Log-file.
The \textit{ModuleManager} holds the path to the plugin libraries. Several paths may be defined here. Due to the fact that the first library fitting to the plugin name is loaded, the order is relevant. The path should be at least assigned to the ARC installation directory. % for the standard MCC are defined here
The next set of tags are holding the name of the plugins to be loaded (line~\ref{lst_code:arched_arcecho_Plugins}).
The names have to correspond to the name of the dynamic libraries within the path defined by the \textit{ModuleManager}.
Finally the chain of the components are declared initiate with the tag \textit{Chain}.
Each component inside the chain is represented by a tag called \textit{Component} which has at least a name attribute.
Its important that a plugin has been loaded which provides the functionality of it.
Depending on the component certain additional tags may be defined inside of it.
\task{Internet Protocol is required.}
The first component of the chain is the \textit{tcp.service}. As to be seen the port 60000 gets assigned for the server to listen to.
The stream which is received by this component is passed to the component defined by the \textit{next} tag.
In that case the will be passed to the component with the \textit{id} atrribute named \textit{http}. According to this manner the message will be passed to higher layers until it reaches the \textit{Plexer}  Depending on the path of the URL which was demanded by the HTTP the Plexer multiplexes the request to the right Web Service. The path is declared within the \textit{next} tag is a regular expression and leads to the service with the id named \textit{echo}. 
Which means that the service will be now reachable under URL \textit{http://localhost:60000/echo}.
This service finally will process the message and create a new message which will be returned all the way back to the TCP layer. The Echo Web Service itself is provided by the ARC package. Additional fix parameters can be passed by assigning tags which have to be known to the Web Service.
The tags \textit{echo:prefix} and \textit{echo:suffix} seen in this example are defining the characters which will enclose the echo  returned string.
\task{The images of the HED structure always are ordered like: TCP - TLS - HTTP - PLEXER - SOAP - WEB SERVICE   but the source code examples are: TCP - TLS - HTTP - SOAP - PLEXER - WEB SERVICE}\\

### 2009-02-19 doc/ws-programming-tutorial/doc/tex_timeservice/timeservice.tex
Pushed the state of the chapter time service a little bit further - added a comment in introduction - modified some source code to have LaTeX labels

In Arc-1 the services are implementated as plugins such that they can easily be included by modifiying the HED configuration file as it was to be seen in Listing~\ref{lst:arched_arcecho_xml}.
The Listing~\ref{lst:time_arched_cpp}.shows the implementation of the time service plugin.
The proper class definition is defined in the corresponding header file which isn't shown here.
The key element for each plugin is the struct PluginDescriptor named PLUGINS\_TABLE\_NAME, see line\ref{lst_code:time_cpp_ptn}. 
%The struct defines basic entities of the service and provides a pointer to the method which is able to create an instance of the time service plugin. 
Within the struct a unique plugin name, the type of the plugin, its version and the pointer to the function which returns the time service instance has to be defined.
The function which returns the pointer to an instance of the service needs to have the PluginArgument as a parameter. 
The actual Time Web Service is implemented within the namespace ArcService. The constructor can be found in line~\ref{lst_code:time_cpp_constructor}, the deconstructor in line~\ref{lst_code:time_cpp_deconstructor} and the method required by the inherited class \textit{Service} file in line~\ref{lst_code:time_cpp_process}. For the Time service is very simple, only the function process needs to be implemented. It gets the incoming and the outgoing message as references and returns a class representing the status the service achieved. 
\lstsetCPP
\lstinputlisting
	[
	label=lst:time_arched_cpp,
	caption={[C++ implementation of the time service. Filename: timeservice.cpp]
	\textbf{C++ implementation of the time service. Filename: timeservice.cpp\textcolor{white}{hmf}}}
	]
{../src/services/timeservice/timeservice.cpp}
The service first determines the current time and than creates a SOAP message using the object \textit{PayloadSOAP} on line~\ref{lst_code:time_cpp_process_payloadSOAP}. The class \textit{PayloadSOAP} is able to create a XML message which is conform to the SOAP protocol (The apperance of the generated request and response will be discussed later). I case of the presented time service the payload consists out of two elements nested into one another. The element \textit{text} holds the element child which again holds the string containing the current time.
Within the line~\ref{lst_code:time_cpp_process_message_payload} the payload is passed to the message. 
The message processing is now completed and the function returns its success status on line~\ref{lst_code:time_cpp_return}.\\

After the service has been implemented, it needs to be loaded into the HED. A suitable HED configuration file is to be seen in Listing~\ref{lst:time_arched_xml}.

\lstsetARCHEDXML
\begin{minipage}[t]{\textwidth}
\lstinputlisting
	[
	label=lst:time_arched_xml,
	caption={[HED configuration for the time service. Filename: arched\_timeservice.xml]
	\textbf{HED configuration for the time service. Filename: arched\_timeservice.xml\textcolor{white}{hmf}}}
	]
{../src/services/timeservice/arched_timeservice.xml}
\end{minipage}

@@

\lstsetCPP
\lstinputlisting
	[
	label=lst:arcecho_arched_xml,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/clients/timeclient/timeclient.cpp}

\lstsetKSH
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:invokation_arched_timeservice,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ arched -c arched_timeservice.xml  && echo jo ||echo n
\end{lstlisting}
\end{minipage}

@@

\lstsetJUSTXML
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:timeservice_cpp_source,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:time="urn:time" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <time>
      <timeRequest></timeRequest>
    </time>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
\end{minipage}

\lstsetJUSTXML
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:timeservice_cpp_source,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <time>
      <timeResponse>Wed Feb 18 11:20:30 2009</timeResponse>
    </time>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
\end{minipage}

>>>>

In Arc-1 the services are implementated as plugins such that they can easily be included by modifiying the HED configuration file as it was to be seen in Listing~\ref{lst:arched_arcecho_xml}.
The Listing~\ref{lst:time_arched_cpp}.shows the implementation of the time service plugin.
The proper class definition is defined in the corresponding header file which isn't shown here.
The key element for each plugin is the struct PluginDescriptor named PLUGINS\_TABLE\_NAME, see line\ref{lst_code:time_cpp_ptn}. 
%The struct defines basic entities of the service and provides a pointer to the method which is able to create an instance of the time service plugin. 
Within the struct a unique plugin name, the type of the plugin, its version and the pointer to the function which returns the time service instance has to be defined.
The function which returns the pointer to an instance of the service needs to have the PluginArgument as a parameter. 
The actual Time Web Service is implemented within the namespace ArcService. The constructor can be found in line~\ref{lst_code:time_cpp_constructor}, the deconstructor in line~\ref{lst_code:time_cpp_deconstructor} and the method required by the inherited class \textit{Service} file in line~\ref{lst_code:time_cpp_process}. For the Time service is very simple, only the function process needs to be implemented. It gets the incoming and the outgoing message as references and returns a class representing the status the service achieved. 
\lstsetCPP
\lstinputlisting
	[
	label=lst:time_arched_cpp,
	caption={[C++ implementation of the time service. Filename: timeservice.cpp]
	\textbf{C++ implementation of the time service. Filename: timeservice.cpp}}
	]
{../src/services/timeservice/timeservice.cpp}
The service first determines the current time and than creates a SOAP message using the object \textit{PayloadSOAP} on line~\ref{lst_code:time_cpp_process_payloadSOAP}. The class \textit{PayloadSOAP} is able to create a XML message which is conform to the SOAP protocol (The apperance of the generated request and response will be discussed later). I case of the presented time service the payload consists out of two elements nested into one another. The element \textit{text} holds the element child which again holds the string containing the current time.
Within the line~\ref{lst_code:time_cpp_process_message_payload} the payload is passed to the message. 
The message processing is now completed and the function returns its success status on line~\ref{lst_code:time_cpp_return}.
The source code has to be compiled to a dynamic library named \textit{libtimeservice.so}.\\

After the service has been implemented and compiled, it needs to be loaded into the HED. A suitable HED configuration file is to be seen in Listing~\ref{lst:time_arched_xml}. 
\lstsetARCHEDXML
\begin{program}
\lstinputlisting
	[
	label=lst:time_arched_xml,
	caption={[HED configuration for the time service. Filename: arched\_timeservice.xml]
	\textbf{HED configuration for the time service. Filename: arched\_timeservice.xml}}
	]
{../src/services/timeservice/arched_timeservice.xml}
\end{program}
A new path element has been introduced into the element \textit{ModuleMananger}, line~\ref{lst_code:arched_time_moduleManager}. It assigns the location to the compliled dynamic library. 
On line~\ref{lst_code:arched_time_plugin} the library is explict mentioned to be loaded.
Another important change has been done within the \textit{Plexer} element in line~\ref{lst_code:arched_time_plexer_next}. A rule has been introduced which redirects the request to the Time Web Service, if the path of URL is \textit{time}.\\

\lstsetKSH
\begin{program}
\begin{lstlisting}[
label=lst:invokation_arched_timeservice,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ arched -c arched_timeservice.xml && echo Daemon started || echo Daemon start failed
\end{lstlisting}
\end{program}

@@

\lstsetCPP
\lstinputlisting
	[
	label=lst:arcecho_time_client_cpp,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/clients/timeclient/timeclient.cpp}

@@

\lstsetJUSTXML
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:arched_time_request,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:time="urn:time" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <time>
      <timeRequest></timeRequest>
    </time>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
\end{minipage}

\lstsetJUSTXML
\begin{minipage}[t]{\textwidth}
\begin{lstlisting}[
label=lst:arched_time_response,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <time>
      <timeResponse>Wed Feb 18 11:20:30 2009</timeResponse>
    </time>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
\end{minipage}
